% Modern C 中的要点清单
\documentclass[UTF8,11pt,a4paper]{ctexart}

% 导言
\title{Takeaways}
\author{Jens Gustedt}

\usepackage{pifont}          % 使用打勾图标
\usepackage{geometry}
\geometry{left=22mm,right=24mm,top=2.4cm,bottom=2.2cm}

\usepackage{xcolor}

% 要点条目标签
\newcommand{\ta}[1]{ \noindent\textbf{#1} \ }

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\purple}[1]{\textcolor{purple}{#1}}
\newcommand{\ok}{\red{\ding{52}}}
\newcommand{\xmark}{\red{\ding{55}}}

\usepackage{listings}

\begin{document}

\begin{center}	\LARGE\purple{Takeaways} \end{center}

\ta{A} \textit{C} and \textit{C++} are different: don't mix them, and don't mix them up. \ok

\ta{B} Don't panic. \ok

\ta{C} All \textit{C} code must be readable.

\ta{D} Premature optimization is the root of all evit. \green{—— Knuth}

\ta{E} Don't speculate about the performance of code; verify it rigorously.

\section*{Level 0 \ Encounter}

\ta{1} \ C is an \textbf{imperative} programming language.

\ta{2} \ C is a compiled programming language.

\ta{3} \ A correct C program is \textbf{portable} between different platforms.

\ta{4} \ A C program should compile cleanly without warnings.

\ta{5} \ Punctuation characters can be used with several different meanings.

\ta{6} \ All identifiers in a program have to be declared.

\ta{7} \ Identifiers may have several consistent declarations.

\ta{8} \ Declarations are bound to the scope in which they appear.

\ta{9} \ Declarations specify identifiers, whereas definitions specify objects.

\ta{10} An object is defined at the same time it is initialized.

\ta{11} Missing elements in initializers default to 0.

\ta{12} For an array with $n$ elements, the first element has index 0, and the last has index $n-1$.

\ta{13} Each object or function must have exactly one definition.

\ta{14} Domain iterations should be coded with a \lstinline|for| statement.

\ta{15} The loop variable should be defined in the initial part of a \lstinline|for|.

\section*{Level 1 \ Acquaintance}



\end{document}